---
title: "Animation with gganimate package"
author: "Mir Afzal"
date: "today"
format: 
    pdf:
      documentclass: scrartcl
      papersize: letter 
---

# Life Expectancy over the years across the Continents 

```{r setup, warning = FALSE, message = FALSE}
#Install Packages
library(ggplot2) # for graphics
library(gganimate) # for moving animation
theme_set(theme_bw())
library(gapminder)
library(tinytex)
library(dplyr)
head(gapminder)
library(magick)

```
```{r}
# Life Expectancy over the Years in Continents 
```{r}
library(ggplot2)
library(gganimate)
theme_set(theme_bw())
library(gapminder)
head(gapminder)
library(tinytex)
```

```{r}
plot4 = gapminder %>% ggplot(
  aes(x = gdpPercap, y=lifeExp, size = pop, colour = country)
) +
  ggtitle("Life Expectancy vs GDP per Capita by Country") +
  labs(x = "GDP Per Capita", 
       y = "Life Expectancy", 
       color = "Continent",
       caption = "Source: Hans Rosling's gapminder data on health and wealth") +
  geom_point(show.legend = FALSE, alpha = 0.7) +
  #scale_color_viridis_d() 
  scale_color_manual(values = country_colors)+
  scale_size(range = c(2, 12)) +
  scale_x_log10() +
  #labelling
  labs(x = "GDP per capita", y = "Life expectancy") 
  
#movement of the time
  plot4 + transition_time(year) +
    #time frame
  labs(title = "Year: {frame_time}") +
    #shadowing the movement
    shadow_wake(wake_length = 0.1, alpha = FALSE) +
    #marking the shadow
    shadow_mark(alpha = 0.3, size = 0.5) + 
    #making frames
    facet_wrap(~continent) +
    view_follow(fixed_y = TRUE) + 
    ease_aes('linear')
```

```{r}
plot1 = gapminder %>% 
  ggplot(aes(x = gdpPercap, y = lifeExp, color = continent, size = pop)) + 
  geom_point(alpha = 0.7, stroke = 0) + 
  theme_fivethirtyeight() +
  scale_size(range = c(2, 12), guide = "none") + 
  scale_x_log10() + 
  
  #labelling
  labs(title = "Life Expectancy vs GDP per Capita by Country",
       x = "GDP Per Capita", 
       y = "Life Expectancy", 
       color = "Continent",
       caption = "Source: Hans Rosling's gapminder data on health and wealth") + 
  #theme
  theme(axis.title = element_text(), 
        text = element_text(family = "serif"), 
        legend.text = element_text(size = 10)) + 
  scale_color_brewer(palette = "Set2")

plot1.animate = plot1 + 
  transition_time(year) + 
  labs(subtitle = "Year: {frame_time}")
plot1.animate
```

